Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
paper: minor fixes

\begin{table}
  \centering
  \input{tables/fcc}
  \caption{Missing value distribution for each attribute in freeCodeCamp Survey Data (\texttt{fcc}}\label{table:fcc-description} 
\end{table}

@@

Our second set of queries is on the freeCodeCamp data (\Cref{fig:queries-fcc}).
\Cref{q6} calculates the average income for higher-income survey participants, grouped by their bootcamp attendance.
\Cref{q7} estimates the average commute time of women from the United States who participated.
\Cref{q8} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q9} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita of countries with and without bootcamp participants over 18 years of age.

>>>>

\begin{table}
  \centering
  \input{tables/fcc}
  \caption{Missing value distribution for each attribute in freeCodeCamp Survey Data (\texttt{fcc})}\label{table:fcc-description} 
\end{table}

@@

Our second set of queries is on the freeCodeCamp data (\Cref{fig:queries-fcc}).
\Cref{q6} calculates the average income for higher-income survey participants, grouped by their bootcamp attendance.
\Cref{q7} estimates the average commute time of women from the United States who participated.
\Cref{q8} calculates the average amount of student debt based on school degree for survey participants who have student debt.
\Cref{q9} joins the freeCodeCamp data with a reference table provided by the World Bank which summarizes GDP per-capita across various countries~\cite{worldbank-data}.
The query calculates the average GDP per-capita by grouping 18+ year old participants who attended bootcamp versus those who did not.
